---
title       : Lifetime Value Prediction
subtitle    : Calculating the Lifetime Value of New Members
author      : John Lee
job         : Nov 22, 2015
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Why LTV?

-  Your marketing team spends millions of dollars on various online campaigns to drive users to your website and signup new members
-  But is the marketing effort and spend worth it? To evaluate, you need to know the LTV of new members!
-  LTV is the forecasted value that new members will generate for your business over their lifetime
-  To be value added, LTV per member should substantially exceed your marketing cost per acquisition (CPA)
-  High growth online businesses achieve: **LTV > 3 x CPA**


--- .class #id 
##  Lifetime Value Predictor

* My new app calculates the predicted LTV of new member cohorts
* LTV is the sum of future cash flows projected forward on an exponentially declining basis, based on the historical performance of past cohorts
* The decay rates are different between members acquired organically versus those from marketing sources
  + Organic LTV (where i is years):
  
    \[\LARGE{LTV = \sum_{i=1}^{15}(ln(i) * -3.509 + Net Revenue_1}\]
  
  + Marketing Sign Ups (where i is years):
  
    \[\LARGE{LTV = \sum_{i=1}^{15}(ln(i) * -1.009 + Net Revenue_1}\]
    
* These decay rates are built into the forecasting model and drive cash flow projections

--- .class #id 
## Example:  Marketing Signups
```{r echo=FALSE}
year <- c(1:15)

typeval <- function(type) {
  switch(type,
         Marketing = -1.099,
         Organic = -3.509)
}

ltvpv <- function(rev_member,disc,exp1) {
  pv <- rep(0,15)
  for (i in 1:15)   {
    pv[i] <- max(log(i) * exp1 + rev_member,0) / (1+(disc/100))^i
  }
  sum(pv)
}

ltv <- function(rev_member,exp1) {
  cf <- rep(0,15)  
  for (i in 1:15)   {
    cf[i] <- max(log(i) * exp1 + rev_member,0)
  }
  sum(cf)
}

cashflows <- function(rev_member,exp1) {
  cf <- rep(0,15)  
  for (i in 1:15)   {
    cf[i] <- max(log(i) * exp1 + rev_member,0)
  }
  cf
}

```
```{r echo=TRUE}
# Let specify key inputs into the LTV model for Marketing Signups: 
type <- "Marketing"  #Type of Signup Cohort (i.e. Organic vs Marketing)
members <-  300000   #Number of members acquired in the quarter
netrev <- 442000     #Net Revenue generated by cohort in the quarter acquired
pct <- 43            #% of Net Revenues in the quarter acquired versus the first year
discount <- 16       #Discount rate % used to calculate the present value of future cashflows
```
```{r echo=FALSE}
ltvpv_pred <- ltvpv(netrev/members/(pct/100),discount,typeval(type))
ltv_pred <- ltv(netrev/members/(pct/100),typeval(type))
```
* LTV = $20.73 per member for Marketing Signups
* On a present value basis, LTV = $10.54 per member.

LTV and PV of LTV:
```{r echo=FALSE}
ltv_pred
ltvpv_pred
```

--- .class #id 
## Cashflows for Marketing Signups
```{r echo=FALSE}
q <- barplot(height=cashflows(netrev/members/(pct/100),typeval(type)),names.arg=year,main="Projected Future Cash Flows",xlab="Years",ylab="Net Revenue per Signup")
```

--- .class #id
